On The Impact of Atoms of Confusion in JavaScript Code

### 2021-05-03 1_Introduction.tex
minor review

Recent work~\cite{DBLP:journals/ese/MedeirosLAAKRG19,DBLP:conf/sigsoft/GopsteinIYDZYC17,Langhout:2021:ACJ} has explored the impact of atoms of confusion on program understanding, and confirmed they negatively impact source code readability. For instance, consider the pair of JavaScript code snippets in Listing~\ref{fig:lst01} (adapted from \textsc{NervJS/taro}). The code at the left-hand side contains two atoms of confusion discussed in previous work focusing on the \clang language~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17}: \emph{Logic as Control Flow} and \emph{Post-increment}. At the right-hand side, we present a clean version of the code, that is, without atoms of confusion. According to the experiments of Gopstein et al.~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17}, removing the atoms \emph{Logic as Control Flow} and \emph{Post-increment} improved the accuracy of program understanding tasks in 41\% and 34\%, respectively.

\begin{figure*}[thb]
\noindent\begin{minipage}{.45\textwidth}  
\begin{lstlisting}[language=JavaScript]
res = properties.reduce((s, b) => {
  b && s++
  return s
}
\end{lstlisting}
\end{minipage}\hfill
\begin{minipage}{.45\textwidth}
\begin{lstlisting}[language=JavaScript]
res = properties.reduce((s, b) => {
  if(b) {
    s = s + 1
  }
  return s
}
\end{lstlisting}
\end{minipage}
\captionof{lstlisting}{Code snippet from \textsc{NervJS/taro} project. Line 2 on the left-hand side of the figure contains two
  atoms of confusion discussed in ~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17}: \emph{Logic
  as Control Flow} and \emph{Post-increment}. On the right-hand side, we present an alternative implementation without atoms of confusion. We could simplify the code on the left-hand side even more, by using \texttt{filter} and \texttt{length} instead of the \texttt{reduce} recursive pattern (e.g., \texttt{res = properties.filter(p => p.length})).}\label{fig:lst01}
\end{figure*}

However, these previous studies focus exclusively on statically typed languages (e.g., \clang, \cpplang, and Java). This way, there is a knowledge gap with respect to the impact of such atoms in dynamic languages such as JavaScript. In this sense, because JavaScript's programming culture differs from that of languages such as \clang and \cpplang, particularly due to the JavaScript's dynamic capabilities and weaker type system, we may find that idioms and constructs that are atoms of confusion in those languages are not particularly difficult to understand for JavaScript programmers and vice-versa. Also, besides being the most widely used language for web development and the most often adopted language on GitHub~\cite{BugsJS:ICST}, JavaScript contains features that combined make the source code fertile ground for errors~\cite{BugsJS:ICST,ClientSideBugsJS:TSE} and confusion~\cite{JSGoodParts:book}.
%, such as weakly typed language~\cite{DynamicBehaviorJS:PLDI}, object-oriented, functional,
% and imperative constructs~\cite{JS-CodeSmells:SCAM}, and features such as run-time
% evaluation~\cite{BugsJS:ICST,ClientSideBugsJS:TSE}, and asynchronous operations.

>>>>

Recent work~\cite{DBLP:journals/ese/MedeirosLAAKRG19,DBLP:conf/sigsoft/GopsteinIYDZYC17,Langhout:2021:ACJ} has explored the impact of atoms of confusion on program understanding, and confirmed they negatively impact source code readability. For instance, consider the pair of JavaScript code snippets in Listing~\ref{fig:lst01} (adapted from \textsc{NervJS/taro}). The code at the left-hand side contains two atoms of confusion discussed in previous work focusing on the \clang language~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17}: Logic as Control Flow and Post-increment. At the right-hand side, we present a clean version of the code, that is, without atoms of confusion. According to the experiments of Gopstein et al.~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17}, removing the atoms Logic as Control Flow and Post-increment improved the accuracy of program understanding tasks in 41\% and 34\%, respectively.

\begin{figure*}[thb]
\noindent\begin{minipage}{.45\textwidth}  
\begin{lstlisting}[language=JavaScript]
res = properties.reduce((s, b) => {
  b && s++
  return s
}
\end{lstlisting}
\end{minipage}\hfill
\begin{minipage}{.45\textwidth}
\begin{lstlisting}[language=JavaScript]
res = properties.reduce((s, b) => {
  if(b) {
    s = s + 1
  }
  return s
}
\end{lstlisting}
\end{minipage}
\captionof{lstlisting}{Code snippet from \textsc{NervJS/taro} project. Line 2 on the left-hand side of the figure contains two
  atoms of confusion discussed in ~\cite{DBLP:conf/sigsoft/GopsteinIYDZYC17}: Logic
  as Control Flow and Post-increment. On the right-hand side, we present an alternative implementation without atoms of confusion. We could simplify the code on the left-hand side even more, by using \texttt{filter} and \texttt{length} instead of the \texttt{reduce} recursive pattern (e.g., \texttt{res = properties.filter(p => p.length})).}\label{fig:lst01}
\end{figure*}

Nonetheless, these previous studies focus exclusively on statically typed languages (e.g., \clang, \cpplang, and Java). This way, there is a knowledge gap with respect to the impact of such atoms in dynamic languages such as JavaScript. In this sense, because JavaScript's programming culture differs from that of languages such as \clang and \cpplang, particularly due to the JavaScript's dynamic capabilities and weaker type system, we may find that idioms and constructs that are atoms of confusion in those languages are not particularly difficult to understand for JavaScript programmers and vice-versa. Also, besides being the most widely used language for web development and the most often adopted language on GitHub~\cite{BugsJS:ICST}, JavaScript contains features that combined make the source code fertile ground for errors~\cite{BugsJS:ICST,ClientSideBugsJS:TSE} and confusion~\cite{JSGoodParts:book}.
%, such as weakly typed language~\cite{DynamicBehaviorJS:PLDI}, object-oriented, functional,
% and imperative constructs~\cite{JS-CodeSmells:SCAM}, and features such as run-time
% evaluation~\cite{BugsJS:ICST,ClientSideBugsJS:TSE}, and asynchronous operations.
